I would like to express my gratitude to everyone who took part in the process of this thesis and in the experiment in general. It has been a pleasure working with so many brilliant and dedicated individuals and I have enjoyed being part of the Quantop group at the Niels Bohr Institute for the past few years.
\\
\\
\noindent
A special thanks to:
\\
\noindent
Eugene Polzik for opening the door and letting me be a part of the Quantop group and for igniting my initial interest in quantum optics and optomechanics.
\\
\\
\noindent
Albert Schlie{\ss}er for always having his door open for discussions and providing much needed guidance even in moments of doubt.
\\
\\
\noindent
William Nielsen for being a brilliant mentor from the very beginning and towards the end being priceless in every possible way.
\\
\\
\noindent
Christoffer Moeller for many inspiring discussions and providing great long distance help.
\\
\\
\noindent
Yeghishe Tsaturyan for being my dear friend all the way through university and for carrying me across the finish line.
\\
\\
\noindent
Andreas Barg for always being ready to help out when needed and for being a great office buddy.
\\
\\
\noindent
Anders Simonsen for the late night advice while pulling an all-nighter.
\\
\\
\noindent
Jörg Müller for being Jörg. Every lab should have a Jörg.
\\
\\
\noindent
Stefan Christensen, Jean-Baptiste Benguin, Jürgen Appel, Anreas Naesby, Tolga Bagci, Rodrigo Thomas, Eva Bookjans, Koji Usami, Georgios Vasilakis, Heidi Soerensen, Kasper Jensen, Dennis Wistisen and of course the rest of the Quantop staff.